Exploratory Analysis

### 2023-11-30 Code/Draft1Rmd.Rmd
knit warnings upated Draft1Rmd.Rmd
density description Draft1Rmd.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

@@

We compared the parallel trends of overdose deaths per-capita in all states. Pre-treatment shows (2016-2020) shows

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

@@

We compared the parallel trends of overdose deaths per-capita in all states using stacked kernel density plots. Pre-treatment shows (2016-2020) fairly similar trends, especially in Oregon and Washington. California has the highest proportion of overdoses in all years.

``` {r warnings = FALSE, fig.height=5, fig.width= 10 }
# Show deaths per-capita for each state
data2 <- health_ranking |>
  mutate(od_deaths_percapita = combined_overdose_deaths / population)

data2 |>
  filter(year %in% c(2016, 2018, 2020, 2022) & !is.na(od_deaths_percapita)) |>
  ggplot(aes(od_deaths_percapita, y = after_stat(count), fill = state)) +
  scale_x_continuous(
    trans = "log10",
    labels = scales::label_number(scale = 1e6, suffix = "M")  # Adjust scale based on your data
  ) +
  geom_density(alpha = 0.3, position = "stack", linetype = "solid", linewidth = 1) +  # Use linewidth instead of size
  facet_grid(year ~ .) +
  labs(
    title = "Density Plot of Overdose Deaths Per Capita by State",
    x = "Overdose Deaths Per Capita",
    y = "Count of Overdose Deaths",
    fill = "State"
  ) +
  theme_minimal()  # Customize the theme if needed
